l

### 2020-02-29 random/career_preparation/resume/resume2.tex
update

\textbf{gym-sips: machine learning in sports betting on google cloud}\\ 
\textbullet{Collected $\sim$1000 games of NFL, NHL, NBA, and MLB odds and scores on Linux VMs}\\
\textbullet{Trained/tested LSTM model to predict odds and scores on $\sim$$5\times 10^{5}$ rows of 20 features}\\
\textbullet{Created a discrete and continuous action space gym environment where agent either picks one team to place money on or allocates some amount to each}\\
\textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
\textbullet{Agent learns to hedge across time and returns a positive net reward on test set}

\begin{itemize}
\item \textbf{Tools:} pytorch, gym, spinningup
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips and /gym-sips
\end{itemize}
\textbf{sippyart: variational-autoencoders for music generation}\\ 
\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders running on GPU}\\
\textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
\begin{itemize}
\item \textbf{Tools:} pytorch, torchaudio, torchvision
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sippyart
\end{itemize}

\section{ACTIVITIES}

\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}
%-------------------------------------------------------------------------------

\end{resume}
\(\)\end{document}

>>>>

\textbf{gym-sips: machine learning in sports betting on google cloud}\hfill\\ 
\textbullet{Collected $\sim$1000 games of NFL, NHL, NBA, and MLB odds and scores on Linux VMs}\\
\textbullet{Created discrete and continuous action space gym environment for asset allocation}\\
\textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
\textbullet{Agent learns to hedge across time and returns a positive net reward on test set}

\begin{itemize}
\item \textbf{Tools:} pytorch, gym, spinningup
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips and /gym-sips
\end{itemize}
\textbf{sippyart: variational-autoencoders for music generation}\\ 
\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders running on GPU}\\
\textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
\begin{itemize}
\item \textbf{Tools:} pytorch, torchaudio, torchvision
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sippyart
\end{itemize}
\textbf{codebyhand: applying handwriting recognition}\\ 
\textbullet{Wrote `paint` program that infers EMNIST characters after each stroke and allows transfer learning on own handwriting}\\
\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
\begin{itemize}
\item \textbf{Tools:} pytorch, torchvision, tkinter 
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/codebyhand
\end{itemize}
\section{ACTIVITIES}
\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}
%-------------------------------------------------------------------------------
\end{resume}
\(\)\end{document}
